---
title: "dirr"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Purpose

The `dirr` package can be used to set up a data project with default folders. Additionally, utility functions to compress data files are provided.

## Installation

The `dirr` package can be installed from GitHub using the `devtools` package and the following commands:

```{r, eval = FALSE}
# install.packages("devtools")
library(devtools)

install_github("bgulbis\dirr")
```

## How to Use

### Create project directories

1. Create a new project folder, in RStudio or other
1. Load the `dirr` package
1. Run the `make_dirs` function

```{r, eval = FALSE}
libryar(dirr)

make_dirs()
```

#### Output

The following folders are created by `make_dirs`:

* data/external - any external data, such as data which was manually collected
* data/final - final version of the data used for analysis
* data/raw - original, raw data sets
* data/tidy - tidy version of original data sets
* doc - manuscript and related documents
* explore - exploratory notebooks and figures
* figs - final figures for posters or manuscript
* ref - reference articles for the project
* report - notebook containing data analysis
* src - R script files used to tidy, transform, and aggregate data into the final data set

### Compress data files

1. Load the `dirr` package
1. Run the `gzip_files` function to compress all data files in the `data/raw` directory, or other specified directory

```{r, eval = FALSE}
library(dirr)

gzip_files()
```

* Use the `pattern` argument to specify only certain files for zipping
* Use `ungzip_files` to uncompress all data files

### Batch read and save Rds files

1. Load the `dirr` package
1. Run the `save_rds` function to save all R objects in the Global Environment whose names match the regular expression passed to the `pattern` argument. The directory where the files are saved is specified by the `data.dir` argument
1. Use `get_rds` to load all files in the specified directory.

```{r eval = FALSE}
library(dirr)

# save all objects that begin with "tidy"
save_rds(data.dir = "data/tidy", pattern = "^tidy")

# read all Rds files
get_rds(data.dir = "data/tidy")
```

* Currently, the `file.ext` argument should be left as default.
