---
title: "dirr"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Purpose

The `dirr` package can be used to set up a data project with default folders. Additionally, utility functions to compress data files are provided.

## Installation

The `dirr` package can be installed from GitHub using the `devtools` package and the following commands:

```{r, eval = FALSE}
libryar(devtools)

install_github("bgulbis\dirr")
```

## How to Use

### Create project directories

1. Create a new project folder, in RStudio or other
1. Load the `dirr` package
1. Run the `make_dirs` function

```{r, eval = FALSE}
libryar(dirr)

make_dirs()
```

### Compress data files

1. Load the `dirr` package
1. Run the `gzip_files` function to compress all data files in the `data/raw` directory

```{r, eval = FALSE}
libryar(dirr)

gzip_files()
```

## Output

The following folders are created by `setup.R`:

1. data/external - any external data, such as data which was manually collected
1. data/final - final version of the data used for analysis
1. data/raw - original, raw data sets
1. data/tidy - tidy version of original data sets
1. doc - manuscript and related documents
1. explore - exploratory notebooks and figures
1. figs - final figures for posters or manuscript
1. report - notebook containing data analysis
1. src - R script files used to tidy, transform, and aggregate data into the final data set
